Global Optimization of the Analogue Method by Means of Genetic Algorithms

### 2016-02-15 Genetic algorithms - Journal of Climate/template.tex
Preparing for submission.

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=19pc,angle=0]{figures/fig01.pdf}\\
	\end{center}
	\caption{Genetic Algorithms operational flowchart}
	\label{fig:structure_gas}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=19pc,angle=0]{figures/fig02.pdf}\\
	\end{center}
	\caption{Evolution of the score of the best individuals over generations for the 10 optimizations processed for a given parametrization. The green line (bottom) represents the score of the sequential approach and the blue one (top), the supposed global optimum.}
	\label{fig:gas_evolution_good}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=19pc,angle=0]{figures/fig03.pdf}\\
	\end{center}
	\caption{Same as Fig. \ref{fig:gas_evolution_good}, but for a GAs parametrization considered as less relevant.}
	\label{fig:gas_evolution_bad}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=19pc,angle=0]{figures/fig04.pdf}\\
	\end{center}
	\caption{Influence of the couples selection operators (Table \ref{tab:assessed_couples_selection_operators}) on the optimization performance (improvement of the score). The box extends from the lower to upper quartile values of the data, with a line at the median. The whiskers extend from the box to 1.5 times the interquartile range. Flier points are those past the end of the whiskers. The star represents the median. The gray box highlights the best options.}
	\label{fig:operator_selectcoupl_score}
\end{figure}

\begin{figure*}[t]
	\begin{center}
		\noindent\includegraphics[width=39pc,angle=0]{figures/fig05.pdf}\\
	\end{center}
	\caption{Influence of the chromosome crossover operators (Table \ref{tab:assessed_crossover_operators}) on the optimization performance (improvement of the score). Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:operator_crossover_score}
\end{figure*}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=19pc,angle=0]{figures/fig06.pdf}\\
	\end{center}
	\caption{Influence of the mutation operators (Table \ref{tab:assessed_mutation_operators}) on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:operator_mutation_score}
\end{figure}

\begin{figure*}[t]
	\begin{center}
		\noindent\includegraphics[width=33pc,angle=0]{figures/fig07.pdf}\\
	\end{center}
	\caption{Influence of the mutation operators (Table \ref{tab:assessed_mutation_operators_bis}) on the optimization performance, leaving the optimizer choose the pressure level of the atmospheric circulation analogy (single level of analogy). The predictand is precipitation over a subcatchment in the Swiss Alps (Binn-Simplon region). The red line represents the score of the sequential calibration and the blue line, the score of the optimization without automatic selection of the pressure levels. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:operator_mutation_score_atmlevel}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\noindent\includegraphics[width=33pc,angle=0]{figures/fig08.pdf}\\
	\end{center}
	\caption{Same as Fig. \ref{fig:operator_mutation_score_atmlevel}, but for another region in the Swiss Alps, with different atmospheric influences.}
	\label{fig:operator_mutation_score_rhoneamont}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\noindent\includegraphics[width=33pc,angle=0]{figures/fig09.pdf}\\
	\end{center}
	\caption{Same as Fig. \ref{fig:operator_mutation_score_atmlevel}, but with a second level of analogy on moisture variables.}
	\label{fig:operator_mutation_score_r2}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\noindent\includegraphics[width=33pc,angle=0]{figures/fig10.pdf}\\
	\end{center}
	\caption{Same as Fig. \ref{fig:operator_mutation_score_r2}, but with a preselection on air temperature rather than a fixed calendar window.}
	\label{fig:operator_mutation_score_r4}
\end{figure*}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=11pc,angle=0]{figures/fig11.pdf}\\
	\end{center}
	\caption{Influence of the natural selection operators on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:operator_selectnat_score}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=11pc,angle=0]{figures/fig12.pdf}\\
	\end{center}
	\caption{Influence of the population size on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:option_taillepop_score}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=11pc,angle=0]{figures/fig13.pdf}\\
	\end{center}
	\caption{Influence of the intermediate population (IG) ratio on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:option_popratio_score}
\end{figure}

>>>>

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=19pc,angle=0]{fig01.pdf}\\
	\end{center}
	\caption{Genetic Algorithms operational flowchart}
	\label{fig:structure_gas}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=19pc,angle=0]{fig02.pdf}\\
	\end{center}
	\caption{Evolution of the score of the best individuals over generations for the 10 optimizations processed for a given parametrization. The continuous bottom line represents the score of the sequential approach and the dashed one (top), the supposed global optimum.}
	\label{fig:gas_evolution_good}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=19pc,angle=0]{fig03.pdf}\\
	\end{center}
	\caption{Same as Fig. \ref{fig:gas_evolution_good}, but for a GAs parametrization considered as less relevant.}
	\label{fig:gas_evolution_bad}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=19pc,angle=0]{fig04.pdf}\\
	\end{center}
	\caption{Influence of the couples selection operators (Table \ref{tab:assessed_couples_selection_operators}) on the optimization performance (improvement of the score). The box extends from the lower to upper quartile values of the data, with a line at the median. The whiskers extend from the box to 1.5 times the interquartile range. Flier points are those past the end of the whiskers. The star represents the median. The gray box highlights the best options.}
	\label{fig:operator_selectcoupl_score}
\end{figure}

\begin{figure*}[t]
	\begin{center}
		\noindent\includegraphics[width=39pc,angle=0]{fig05.pdf}\\
	\end{center}
	\caption{Influence of the chromosome crossover operators (Table \ref{tab:assessed_crossover_operators}) on the optimization performance (improvement of the score). Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:operator_crossover_score}
\end{figure*}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=19pc,angle=0]{fig06.pdf}\\
	\end{center}
	\caption{Influence of the mutation operators (Table \ref{tab:assessed_mutation_operators}) on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:operator_mutation_score}
\end{figure}

\begin{figure*}[t]
	\begin{center}
		\noindent\includegraphics[width=33pc,angle=0]{fig07.pdf}\\
	\end{center}
	\caption{Influence of the mutation operators (Table \ref{tab:assessed_mutation_operators_bis}) on the optimization performance, leaving the optimizer choose the pressure level of the atmospheric circulation analogy (single level of analogy). The predictand is precipitation over a subcatchment in the Swiss Alps (Binn-Simplon region). The continuous bottom line represents the score of the sequential calibration and the dashed superior line, the score of the optimization without automatic selection of the pressure levels. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:operator_mutation_score_atmlevel}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\noindent\includegraphics[width=33pc,angle=0]{fig08.pdf}\\
	\end{center}
	\caption{Same as Fig. \ref{fig:operator_mutation_score_atmlevel}, but for another region in the Swiss Alps, with different atmospheric influences.}
	\label{fig:operator_mutation_score_rhoneamont}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\noindent\includegraphics[width=33pc,angle=0]{fig09.pdf}\\
	\end{center}
	\caption{Same as Fig. \ref{fig:operator_mutation_score_atmlevel}, but with a second level of analogy on moisture variables.}
	\label{fig:operator_mutation_score_r2}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\noindent\includegraphics[width=33pc,angle=0]{fig10.pdf}\\
	\end{center}
	\caption{Same as Fig. \ref{fig:operator_mutation_score_r2}, but with a preselection on air temperature rather than a fixed calendar window.}
	\label{fig:operator_mutation_score_r4}
\end{figure*}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=11pc,angle=0]{fig11.pdf}\\
	\end{center}
	\caption{Influence of the natural selection operators on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:operator_selectnat_score}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=11pc,angle=0]{fig12.pdf}\\
	\end{center}
	\caption{Influence of the population size on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:option_taillepop_score}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=11pc,angle=0]{fig13.pdf}\\
	\end{center}
	\caption{Influence of the intermediate population (IG) ratio on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:option_popratio_score}
\end{figure}
